\chapter{System Specifications}
\label{Systems_Specifications}

\section{Introduction}

This chapter translates the qualitative scope statements and design objectives introduced in Chapter~\ref{Introduction} into measurable, verifiable specifications for the two principal subsystems of the full tracking solution: the \gls{OMC} subsystem, comprising the OptiTrack camera network and its supporting software, and the \gls{OCP} subsystem, comprising the genetic algorithm and its cost function. Together these two subsystems form the end-to-end system: the \gls{OCP} algorithm is executed offline to determine the camera configuration, and the resulting arrangement is then deployed for real-time robot tracking by the \gls{OMC} subsystem.

The approach adopted here is informed by NASA systems engineering practice \parencite{nasaSE2017}, in which every requirement is assigned a unique identifier, an importance level, and two acceptance thresholds: a \textit{marginal} value defining the minimum acceptable performance that the system must achieve to fulfil its function, and an \textit{ideal} value defining the target performance under well-optimised conditions. Importance levels are defined as follows:

\begin{itemize}
    \item \textbf{Critical (C)}: The system cannot fulfil its primary function without meeting this requirement.
    \item \textbf{High (H)}: Failure to meet this requirement significantly degrades system effectiveness.
    \item \textbf{Medium (M)}: Desirable for optimal performance; the system remains operational at reduced capacity without it.
    \item \textbf{Low (L)}: Beneficial but not essential; the system meets its primary objectives regardless.
\end{itemize}

Each requirement carries a traceability code. Codes of the form \texttt{S-\textit{XX}} refer to qualitative scope specifications defined in Chapter \ref{Introduction}; codes of the form \texttt{R-\textit{XX}} identify an external source (a manufacturer datasheet, a validated literature result, or an established engineering convention) that provides the quantitative basis for the stated threshold. The complete mapping of reference codes to sources is given in Table \ref{tab:trace-refs}.

Table ref{tab:metrics-overview} provides a consolidated overview of all specified metrics before their detailed treatment in the subsystem sections below.

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.2cm} >{\raggedright\arraybackslash}p{2.6cm} p{1.7cm} p{1.8cm} p{4cm}}
\caption[Overview of all system specification metrics.]{Overview of all system specification metrics.}
\label{tab:metrics-overview}\\
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Subsystem} & \textbf{Category} & \textbf{Purpose} \\
\midrule
\endfirsthead
\multicolumn{5}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Subsystem} & \textbf{Category} & \textbf{Purpose} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\small\textit{(Continued on next page)}}\\
\endfoot
\bottomrule
\endlastfoot
OMC-P-01 & Sensor Resolution        & OMC & Performance & Characterises the spatial sampling capability of each camera, governing minimum detectable marker displacement in the image plane. \\[4pt]
OMC-P-02 & 3D Position Accuracy     & OMC & Performance & Quantifies end-to-end positional error against a known ground-truth reference; sets the foundation for trajectory estimate quality. \\[4pt]
OMC-P-03 & Frame Rate               & OMC & Performance & Temporal resolution of the capture system; must be sufficient to sample fast robotic manoeuvres without aliasing. \\[4pt]
OMC-P-04 & System Latency           & OMC & Performance & Pipeline delay from image capture to pose output; critical for closed-loop controllers that require low-latency state feedback. \\[4pt]
OMC-P-05 & Calibration Residual     & OMC & Performance & Mean ray-convergence offset reported by EasyWand6; a direct indicator of triangulation precision for a given arrangement. \\[4pt]
OMC-P-06 & Marker Reconstruction Completeness & OMC & Performance & Fraction of captured frames in which all markers are successfully resolved; reflects network coverage and redundancy. \\
\midrule
OMC-F-01 & Capture Volume           & OMC & Functional  & Minimum usable 3D volume within which all performance requirements are simultaneously satisfied. \\[4pt]
OMC-F-02 & Maximum Detection Range  & OMC & Functional  & Furthest camera-to-marker distance at which a marker can be reliably detected per lens type. \\[4pt]
OMC-F-03 & Camera Count             & OMC & Functional  & Minimum number of cameras required for multi-view redundancy and 3D reconstruction. \\[4pt]
OMC-F-04 & Setup Footprint          & OMC & Functional  & Constrains the system to fit within the available laboratory space without structural modification. \\[4pt]
OMC-F-05 & System Cost              & OMC & Functional  & Bounds total hardware and software expenditure to within the available research budget. \\[4pt]
OMC-F-06 & Portability              & OMC & Functional  & Ease of disassembly and redeployment without specialist equipment. \\[4pt]
OMC-F-07 & Configurability          & OMC & Functional  & Ability to adjust tracking parameters without hardware modification. \\
\midrule
OCP-P-01 & Workspace Coverage       & OCP & Performance & Fraction of target grid points observed by $\geq 2$ cameras; necessary precondition for triangulation. \\[4pt]
OCP-P-02 & Triangulation Angle Compliance & OCP & Performance & Fraction of target points where $\geq 1$ camera pair satisfies $40\degree \leq \theta \leq 140\degree$ for well-conditioned reconstruction. \\[4pt]
OCP-P-03 & Normalised Resolution Uncertainty & OCP & Performance & Normalised composite cost $J_{\text{res}}/J^{\text{norm}}_{\text{res}}$ quantifying pixel-quantisation-induced 3D position uncertainty across the workspace. \\[4pt]
OCP-P-04 & Mean Dynamic Occlusion Angle & OCP & Performance & Mean angular span per target point from which triangulation fails due to self-occlusion; lower values indicate greater robustness. \\[4pt]
OCP-P-05 & Optimisation Runtime     & OCP & Performance & Wall-clock time for the GA to complete a full run; bounds the pre-deployment computational cost. \\[4pt]
OCP-P-06 & Calibration Residual Improvement & OCP & Performance & Percentage reduction in Motive calibration residual vs.\ the ad-hoc baseline; primary experimental validation metric. \\[4pt]
OCP-P-07 & Marker Reconstruction Improvement & OCP & Performance & Percentage-point increase in reconstruction completeness vs.\ ad-hoc baseline; validates real-world tracking gains. \\
\midrule
OCP-F-01 & Camera Count Scalability & OCP & Functional  & Range of camera counts over which the algorithm produces valid configurations without source-code modification. \\[4pt]
OCP-F-02 & Workspace Parameterizability & OCP & Functional  & Degree to which workspace geometry and camera bounds can be specified as algorithm inputs. \\[4pt]
OCP-F-03 & Solution Repeatability   & OCP & Functional  & Consistency of the algorithm's output cost across independent runs; characterises stochastic variance. \\[4pt]
OCP-F-04 & Output Interface         & OCP & Functional  & Format in which the optimised configuration is exported for use by the \gls{OMC} subsystem. \\[4pt]
OCP-F-05 & Objective Parameterizability & OCP & Functional  & User-adjustable weighting of the resolution and occlusion objectives in the combined cost function. \\
\end{longtable}}

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.0cm} p{1.5cm} p{9.8cm}}
\caption{Reference traceability codes used in the subsystem specification tables.}
\label{tab:trace-refs}\\
\toprule
\textbf{Code} & \textbf{Type} & \textbf{Source} \\
\midrule
\endfirsthead
\toprule
\textbf{Code} & \textbf{Type} & \textbf{Source} \\
\midrule
\endhead
\bottomrule
\endlastfoot
S-01 & Internal & \textit{Ch.~\ref{Introduction}}: The system shall provide real-time 3D position tracking of \gls{UAV} markers within an indoor laboratory flight arena. \\[4pt]
S-02 & Internal & \textit{Ch.~\ref{Introduction}}: The system shall achieve tracking accuracy and reconstruction completeness sufficient to support closed-loop \gls{UAV} flight control. \\[4pt]
S-03 & Internal & \textit{Ch.~\ref{Introduction}}: The \gls{OCP} subsystem shall produce a camera configuration that yields measurably better tracking performance than an ad-hoc arrangement. \\[4pt]
S-04 & Internal & \textit{Ch.~\ref{Introduction}}: The system shall be practically deployable within the constraints of a university research laboratory (space, budget, manpower). \\[4pt]
R-01 & External & OptiTrack camera specification sheet \parencite{OptiTrackDatasheet}. \\[4pt]
R-02 & External & Aurand et al.\ (2017) --- accuracy mapping of a 42-camera OptiTrack Prime 41 system; 97\,\% of capture area below 0.2\,mm error \parencite{aurandAccuracyMapOptical2017}. \\[4pt]
R-03 & External & Nagymát{\'e} \& Kiss (2018) --- review of OptiTrack validation studies; identifies calibration residual thresholds of $<0.5$\,mm (acceptable) and $<0.3$\,mm (excellent) \parencite{nagymateMotionCaptureSystem2018}. \\[4pt]
R-04 & External & Rahimian \& Kearney (2017) --- physical OptiTrack deployment achieved 86\,\% marker reconstruction (optimised) vs.\ 30\,\% (ad-hoc) \parencite{rahimianOptimalCameraPlacement2017}. \\[4pt]
R-05 & External & Ziegler et al.\ (2023) --- triangulation error grows exponentially as convergence angle approaches $0\degree$ or $180\degree$; well-conditioned range $40\degree$--$140\degree$ \parencite{zieglerOptimalCameraPlacement2023}. \\
\end{longtable}}

\section{Overall System Architecture}

The system is composed of two coupled subsystems operating on distinct timescales, as illustrated in Figure~\ref{fig:system-block-diagram}. The \gls{OCP} subsystem runs \textit{offline}, prior to physical deployment: it takes the workspace geometry and camera hardware specifications as inputs and outputs an optimal camera configuration via the genetic algorithm described in Chapter~\ref{OCP}. This configuration is then implemented physically by mounting the cameras at the computed positions and orientations. The \gls{OMC} subsystem then operates \textit{online} in real time: the camera network captures infrared images of passive retroreflective markers attached to the \gls{UAV}, the Motive software reconstructs the 3D marker positions by triangulation, and the resulting pose estimates are streamed to the flight controller at the specified frame rate.

The two subsystems are coupled through the camera configuration: the quality of the \gls{OMC} system's real-time output is directly determined by the geometric arrangement of the cameras, which is the quantity that the \gls{OCP} algorithm seeks to optimise. This coupling is the central motivation for the work presented in this thesis.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    node distance=1.1cm and 2.0cm,
    process/.style={rectangle, rounded corners=3pt, minimum width=3.4cm, minimum height=0.75cm, align=center, draw=black!70, fill=blue!8, font=\small},
    hardware/.style={rectangle, minimum width=3.4cm, minimum height=0.75cm, align=center, draw=black!70, fill=orange!15, font=\small},
    datanode/.style={rectangle, minimum width=3.0cm, minimum height=0.65cm, align=center, draw=black!70, fill=green!12, font=\small},
    externalnode/.style={rectangle, rounded corners=3pt, minimum width=3.4cm, minimum height=0.75cm, align=center, draw=black!70, fill=gray!12, font=\small},
    arrow/.style={-{Stealth[length=2.5mm]}, thick},
    dashedarrow/.style={-{Stealth[length=2.5mm]}, thick, dashed, gray!70},
    grouplabel/.style={font=\small\bfseries, text=black!70},
]
\node (specs)  [process]                                        {Workspace \& Camera\\Specifications};
\node (ga)     [process, below=of specs]                        {GA Optimiser\\(Ch.~\ref{OCP})};
\node (config) [datanode, below=of ga]                          {Optimal Camera\\Configuration};
\draw[arrow] (specs)  -- (ga);
\draw[arrow] (ga)     -- (config);

\node (mount)  [hardware, right=4.5cm of specs, yshift=-0.75cm] {7$\times$ OptiTrack Cameras\\(IR illuminators + sensors)};
\node (motive) [process,  below=of mount]                       {Motive Software\\(Calibration \& 3D Reconstruction)};
\node (pose)   [datanode, below=of motive]                      {3D Pose Estimates\\($\mathbf{x}, \mathbf{q}$ per marker)};
\node (ctrl)   [externalnode, below=of pose]                    {UAV Flight Controller};
\draw[arrow] (mount)  -- (motive);
\draw[arrow] (motive) -- (pose);
\draw[arrow] (pose)   -- (ctrl);

\draw[dashedarrow] (config.east) -- node[above, font=\scriptsize, text=black] {Physical deployment} (mount.west);

\node[grouplabel, above=0.5cm of specs] {OCP Subsystem (Offline)};
\node[grouplabel, above=0.5cm of mount] {OMC Subsystem (Real-Time)};

\begin{scope}[on background layer]
    \node[draw=blue!30, fill=blue!4, rounded corners=5pt,
          fit=(specs)(ga)(config), inner sep=0.45cm] {};
    \node[draw=orange!40, fill=orange!4, rounded corners=5pt,
          fit=(mount)(motive)(pose)(ctrl), inner sep=0.45cm] {};
\end{scope}
\end{tikzpicture}
\caption[Overall system architecture block diagram.]{Overall system architecture. The \gls{OCP} subsystem (left) operates offline to determine the optimal camera placement, which is then physically implemented. The \gls{OMC} subsystem (right) operates in real time to stream 3D pose estimates to the \gls{UAV} flight controller.}
\label{fig:system-block-diagram}
\end{figure}

%----------------------------------------------------------------------------------------
\section{OMC Subsystem Requirements}
%----------------------------------------------------------------------------------------

The \gls{OMC} subsystem is responsible for the physical capture and three-dimensional reconstruction of marker positions within the flight arena. Its specifications are principally informed by the requirements of closed-loop \gls{UAV} control, which demands low-latency, high-frequency, and accurate state feedback, and by the physical characteristics of the OptiTrack hardware deployed. The values below are substantiated by the OptiTrack camera datasheet \parencite{OptiTrackDatasheet} and validated by systematic accuracy studies in the literature \parencite{aurandAccuracyMapOptical2017, nagymateMotionCaptureSystem2018}.

\subsection{Performance Requirements}

Table~\ref{tab:omc-perf-desc} defines each metric; the quantitative thresholds are given in Table~\ref{tab:omc-perf}.

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{3.0cm} p{7.5cm}}
\caption[OMC performance metric definitions.]{OMC performance metric definitions. Quantitative thresholds are given in Table~\ref{tab:omc-perf}.}
\label{tab:omc-perf-desc}\\
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endfirsthead
\multicolumn{3}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\endlastfoot
OMC-P-01 & Sensor Resolution & Minimum imaging array resolution per camera, governing the fineness of marker localisation in the image plane. \\[4pt]
OMC-P-02 & 3D Position Accuracy & Root-mean-square error of reconstructed marker positions against an external dimensional reference at representative locations across the capture volume. \\[4pt]
OMC-P-03 & Frame Rate & Temporal sampling rate of the camera system. Must be sufficient to capture maximum \gls{UAV} velocities without spatial aliasing or motion blur. \\[4pt]
OMC-P-04 & System Latency & End-to-end pipeline delay from image acquisition to 3D pose availability at the flight controller. Directly constrains the bandwidth of any feedback loop using \gls{OMC} state estimates. \\[4pt]
OMC-P-05 & Calibration Residual & Mean ray-convergence offset (mm) reported by Motive following the wanding calibration procedure. Reflects geometric consistency of the camera network and triangulation precision. \\[4pt]
OMC-P-06 & Marker Reconstruction Completeness & Fraction of captured frames in which all markers in the rigid body are successfully resolved. Values below the marginal threshold render continuous trajectory estimation unreliable. \\
\end{longtable}}

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{1.8cm} p{0.7cm} p{1.0cm} p{2.0cm} p{2.0cm}}
\caption[OMC subsystem performance specifications.]{OMC subsystem performance specifications. Importance: C\,=\,Critical, H\,=\,High, M\,=\,Medium, L\,=\,Low. Metric definitions are given in Table~\ref{tab:omc-perf-desc}.}
\label{tab:omc-perf}\\
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endfirsthead
\multicolumn{6}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endhead
\midrule
\multicolumn{6}{r}{\small\textit{(Continued on next page)}}\\
\endfoot
\bottomrule
\endlastfoot
OMC-P-01 & S-01, R-01 & H & MP & $\geq 1.3$ & $\geq 1.7$ \\[4pt]
OMC-P-02 & S-02, R-02 & C & mm\,(RMS) & $< 1.0$ & $< 0.3$ \\[4pt]
OMC-P-03 & S-02, R-01 & H & fps & $\geq 120$ & $\geq 240$ \\[4pt]
OMC-P-04 & S-02, R-01 & H & ms & $< 10$ & $< 5.5$ \\[4pt]
OMC-P-05 & S-02, R-03 & H & mm & $< 0.5$ & $< 0.3$ \\[4pt]
OMC-P-06 & S-02, R-04 & C & \% & $> 90$ & $> 99$ \\
\end{longtable}}

\subsection{Functional Requirements}

Table~\ref{tab:omc-func-desc} defines each metric; the quantitative thresholds are given in Table~\ref{tab:omc-func}.

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{3.0cm} p{7.5cm}}
\caption[OMC functional metric definitions.]{OMC functional metric definitions. Quantitative thresholds are given in Table~\ref{tab:omc-func}.}
\label{tab:omc-func-desc}\\
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endfirsthead
\multicolumn{3}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\endlastfoot
OMC-F-01 & Capture Volume & Usable 3D volume in which all performance requirements (OMC-P-01 to OMC-P-06) are simultaneously satisfied. Defines the flight envelope available to the \gls{UAV}. \\[4pt]
OMC-F-02 & Maximum Detection Range & Maximum camera-to-marker distance at which a standard 12\,mm retroreflective marker can be reliably detected for each lens type. \\[4pt]
OMC-F-03 & Camera Count & Minimum number of cameras required to simultaneously achieve the prescribed coverage and accuracy requirements across the full capture volume. \\[4pt]
OMC-F-04 & Setup Footprint & Maximum floor area and ceiling height required for system installation. Must not exceed the dimensions of the available laboratory space. \\[4pt]
OMC-F-05 & System Cost & Total expenditure on camera hardware, cabling, networking, and licensing. Must remain within the available research project budget. \\[4pt]
OMC-F-06 & Portability & Ease with which the camera network can be disassembled and redeployed. Mounts should not require permanent structural fixings. \\[4pt]
OMC-F-07 & Configurability & Degree to which capture parameters (frame rate, exposure, marker profiles) can be adjusted by the user via software without hardware modification. \\
\end{longtable}}

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{1.8cm} p{0.7cm} p{1.0cm} p{2.8cm} p{2.8cm}}
\caption[OMC subsystem functional specifications.]{OMC subsystem functional specifications. Metric definitions are given in Table~\ref{tab:omc-func-desc}.}
\label{tab:omc-func}\\
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endfirsthead
\multicolumn{6}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endhead
\midrule
\multicolumn{6}{r}{\small\textit{(Continued on next page)}}\\
\endfoot
\bottomrule
\endlastfoot
OMC-F-01 & S-01 & C & m$^3$ & $\geq 256$\newline $(8{\times}8{\times}4)$ & Full room volume \\[4pt]
OMC-F-02 & S-01, R-01 & H & m & $\geq 9$ (wide) & $\geq 16$ (narrow) \\[4pt]
OMC-F-03 & S-02, S-04 & H & cameras & $\geq 4$ & $\geq 7$ \\[4pt]
OMC-F-04 & S-01, S-04 & M & m$^2$\,/\,m & $\leq 90$\,m$^2$; ceiling $\leq 5$\,m & Adaptable to varied rooms \\[4pt]
OMC-F-05 & S-04 & M & --- & Within project budget & Minimised subject to meeting OMC-P-01--06 \\[4pt]
OMC-F-06 & S-04 & L & --- & Mounts removable without specialist tools & Single-person redeployment in $< 4$\,h \\[4pt]
OMC-F-07 & S-03, S-04 & M & --- & All parameters user-adjustable in Motive & Full API-level control; compatible with OCP algorithm output \\
\end{longtable}}

%----------------------------------------------------------------------------------------
\section{OCP Subsystem Requirements}
%----------------------------------------------------------------------------------------

The \gls{OCP} subsystem is the offline computational tool that determines the camera configuration to be physically implemented. Its performance requirements are defined at two levels: \textit{internal} metrics that characterise the quality of the solution produced by the algorithm relative to the simulation model (OCP-P-01 through OCP-P-05), and \textit{external} or verification metrics that characterise the real-world improvement when the optimised configuration is deployed on the physical system (OCP-P-06 and OCP-P-07). The internal metrics derive directly from the cost function components developed in Section~\ref{sec:cost-function}, namely the resolution uncertainty model of Wu, Sharma, and Huang \parencite{sharmaAnalysisUncertaintyBounds1998} and the dynamic occlusion model of Rahimian and Kearney \parencite{rahimianOptimalCameraPlacement2017}. The external metrics follow the experimental validation framework described in Section~\ref{sec:verification}.

\subsection{Performance Requirements}

Table~\ref{tab:ocp-perf-desc} defines each metric; the quantitative thresholds are given in Table~\ref{tab:ocp-perf}. Internal metrics (OCP-P-01 to OCP-P-05) characterise simulation-domain solution quality; external metrics (OCP-P-06 and OCP-P-07) characterise real-world improvement.

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{3.2cm} p{7.3cm}}
\caption[OCP performance metric definitions.]{OCP performance metric definitions. Quantitative thresholds are given in Table~\ref{tab:ocp-perf}.}
\label{tab:ocp-perf-desc}\\
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endfirsthead
\multicolumn{3}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\endlastfoot
OCP-P-01 & Workspace Coverage & Fraction of discrete target-space grid points observed by $\geq 2$ cameras simultaneously. A point visible to fewer than two cameras cannot be triangulated. \\[4pt]
OCP-P-02 & Triangulation Angle Compliance & Fraction of target grid points for which $\geq 1$ camera pair satisfies $40\degree \leq \theta_{ij} \leq 140\degree$. Configurations violating this constraint produce ill-conditioned depth estimates even when the point is visible. \\[4pt]
OCP-P-03 & Normalised Resolution Uncertainty & Normalised cost $J_{\text{res}} / J^{\text{norm}}_{\text{res}}$ (Eq.~\ref{eq:combined-cost}). $J^{\text{norm}}_{\text{res}} = 100$ is the approximate cost of a random configuration; values below 1.0 represent improvement over the unoptimised baseline. \\[4pt]
OCP-P-04 & Mean Dynamic Occlusion Angle & Mean angular span per target point (degrees) from which the target cannot be triangulated under the dynamic occluder model (Eq.~\ref{eq:occlusion-point}). Lower values indicate greater robustness to arbitrary occluder orientations. \\[4pt]
OCP-P-05 & Optimisation Runtime & Wall-clock time to complete a full run of $G_{\max}$ generations on the available parallel hardware. Bounds the pre-deployment time cost of running the optimiser. \\[4pt]
OCP-P-06 & Calibration Residual Improvement & Percentage reduction in Motive calibration residual (mm) achieved by the optimised configuration relative to the ad-hoc baseline, using identical wanding protocol and capture volume. \\[4pt]
OCP-P-07 & Marker Reconstruction Improvement & Increase in marker reconstruction completeness (percentage points) achieved by the optimised vs.\ ad-hoc configuration. Analogous to the 56\,pp improvement demonstrated by Rahimian and Kearney \parencite{rahimianOptimalCameraPlacement2017}. \\
\end{longtable}}

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{2.0cm} p{0.7cm} p{1.5cm} p{1.8cm} p{1.5cm}}
\caption[OCP subsystem performance specifications.]{OCP subsystem performance specifications. Importance: C\,=\,Critical, H\,=\,High, M\,=\,Medium, L\,=\,Low. Metric definitions are given in Table~\ref{tab:ocp-perf-desc}.}
\label{tab:ocp-perf}\\
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endfirsthead
\multicolumn{6}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endhead
\midrule
\multicolumn{6}{r}{\small\textit{(Continued on next page)}}\\
\endfoot
\bottomrule
\endlastfoot
OCP-P-01 & S-02, S-03, R-04 & C & \% & $> 90$ & $> 99$ \\[4pt]
OCP-P-02 & S-02, S-03, R-05 & C & \% & $> 80$ & $> 95$ \\[4pt]
OCP-P-03 & S-03 & H & (dimensionless) & $< 0.5$ & $< 0.3$ \\[4pt]
OCP-P-04 & S-03, R-04 & H & degrees & $< 120$ & $< 60$ \\[4pt]
OCP-P-05 & S-03, S-04 & H & min & $< 60$ & $< 30$ \\[4pt]
OCP-P-06 & S-02, S-03, R-03 & H & \% red. & $\geq 20$ & $\geq 50$ \\[4pt]
OCP-P-07 & S-02, S-03, R-04 & H & pp & $\geq 20$ & $\geq 50$ \\
\end{longtable}}

\subsection{Functional Requirements}

Table~\ref{tab:ocp-func-desc} defines each metric; the quantitative thresholds are given in Table~\ref{tab:ocp-func}.

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{3.2cm} p{7.3cm}}
\caption[OCP functional metric definitions.]{OCP functional metric definitions. Quantitative thresholds are given in Table~\ref{tab:ocp-func}.}
\label{tab:ocp-func-desc}\\
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endfirsthead
\multicolumn{3}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Metric} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\endlastfoot
OCP-F-01 & Camera Count Scalability & Range of camera counts for which the algorithm, chromosome representation (Eq.~\ref{eq:chromosome}), and cost function produce valid optimised configurations without source-code modification. \\[4pt]
OCP-F-02 & Workspace Parameterizability & Degree to which the workspace geometry, camera mounting bounds, and target-space grid resolution can be configured by the user as algorithm inputs without modifying source code. \\[4pt]
OCP-F-03 & Solution Repeatability & Consistency of the optimised cost $f^*$ across independent runs with different random seeds. Characterises stochastic variance and bounds the reliability of the solution quality claim. \\[4pt]
OCP-F-04 & Output Interface & Format in which the algorithm exports the optimal configuration $\mathbf{c}^*$ for physical implementation and potential import into the \gls{OMC} software. \\[4pt]
OCP-F-05 & Objective Weight Parameterizability & User-adjustable weighting of $w_{\text{res}}$ and $w_{\text{occ}}$ in the combined cost function (Eq.~\ref{eq:combined-cost}), allowing the designer to bias the optimiser toward precision or occlusion robustness. \\
\end{longtable}}

{\small\setlength{\tabcolsep}{4pt}
\begin{longtable}{p{1.5cm} p{1.8cm} p{0.7cm} p{1.0cm} p{3.2cm} p{2.8cm}}
\caption[OCP subsystem functional specifications.]{OCP subsystem functional specifications. Metric definitions are given in Table~\ref{tab:ocp-func-desc}.}
\label{tab:ocp-func}\\
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endfirsthead
\multicolumn{6}{l}{\small\textit{(Continued from previous page)}}\\[2pt]
\toprule
\textbf{ID} & \textbf{Trace} & \textbf{Imp.} & \textbf{Units} & \textbf{Marginal} & \textbf{Ideal} \\
\midrule
\endhead
\midrule
\multicolumn{6}{r}{\small\textit{(Continued on next page)}}\\
\endfoot
\bottomrule
\endlastfoot
OCP-F-01 & S-04 & M & cameras & $4 \leq k \leq 10$ & Any $k \geq 4$ \\[4pt]
OCP-F-02 & S-03, S-04 & M & --- & Accepts user-defined rectangular workspace dimensions and camera placement bounds & Supports arbitrary convex workspace geometry \\[4pt]
OCP-F-03 & S-03 & M & \%\,CV & $\leq 15$ & $\leq 5$ \\[4pt]
OCP-F-04 & S-03, S-04 & M & --- & Exports $(x,y,z)$ and $(\alpha,\beta,\gamma)$ per camera in a structured file (\texttt{.csv} or \texttt{.mat}) & Direct numerical import into Motive layout interface \\[4pt]
OCP-F-05 & S-03 & M & --- & User-configurable $w_{\text{res}}, w_{\text{occ}} \geq 0$,\newline $w_{\text{res}} + w_{\text{occ}} = 1$ & Extendable to $n$-objective framework \\
\end{longtable}}

%----------------------------------------------------------------------------------------
\section{Constraints and Assumptions}
%----------------------------------------------------------------------------------------

The specifications above are defined subject to the following constraints and assumptions, which bound the scope of the system and its verification:

\begin{enumerate}

    \item \textbf{Indoor rectangular workspace.} The system is designed for a single indoor room with a flat ceiling and clear floor. The target space is a rectangular volume of $8 \times 8 \times 4$\,m, corresponding to the bounds $[-4, 4] \times [-4, 4] \times [0, 4]$\,m in the world frame.

    \item \textbf{Passive retroreflective marker tracking.} The \gls{OMC} subsystem is assumed to track passive infrared-retroreflective markers (12\,mm diameter) attached to the \gls{UAV}. The specifications do not apply to markerless pose estimation or active LED markers.

    \item \textbf{Wall- and ceiling-mounted cameras.} Camera positions are constrained to the four walls and the ceiling (the floor is excluded, since a floor-mounted camera oriented upward contributes negligibly to coverage of the flight volume). The mounting bounds match the OCP algorithm search space: $[-5, 5] \times [-4.5, 4.5] \times [0, 4.8]$\,m (Section~\ref{sec:algorithm-config}).

    \item \textbf{Controlled infrared environment.} The specifications assume a laboratory prepared to minimise infrared noise: windows covered or blacked out, highly reflective surfaces minimised, and no competing high-brightness IR sources within the camera fields of view.

    \item \textbf{Static workspace structure.} Obstacles within the capture volume are assumed to be static for the purposes of the \gls{OCP} model. Dynamic occlusion arising from the \gls{UAV} body itself is captured by the dynamic occluder model (OCP-P-04), but moving people or additional vehicles are not modelled.

    \item \textbf{Offline optimisation paradigm.} The \gls{OCP} algorithm is run once prior to physical deployment and does not adapt in real time to camera failures or workspace changes. Re-optimisation is required if the room geometry or camera count changes.

    \item \textbf{Pinhole camera model.} The cost function assumes ideal pinhole projection without lens distortion. In physical deployment, residual post-calibration distortion is assumed negligible relative to the pixel-quantisation uncertainty captured by the resolution model.

    \item \textbf{Seven-camera configuration.} The primary specifications are defined for the $k = 7$ camera system (three wide-angle, four narrow-angle lenses) available for this work. Scalability bounds (OCP-F-01) reflect the validated range of the current implementation.

\end{enumerate}
